Influences on the access to higher education: Visualization and modeling for Chilean data

### 2021-10-24 Paper_Higher_Education.Rmd
Add files via upload

reg <- within(reg, ESTADO <- relevel(ESTADO, ref = "No Matriculado"))
reg = reg %>% filter(EDAD %in% c('16','17','18','19'))
reg <- within(reg, COD_DEPE2 <- relevel(COD_DEPE2, ref = "Municipal"))

m_logit <- multinom(ESTADO ~ EDAD  + NEM + GEN_ALU + 
                 COD_DEPE2 + factor(PostBeca) + factor(PERCENTIL) + factor(NOMBRE_REGION) + AGNO_EGRESO, data = reg)

@@

#Coeficientes of the table.
#command Summary takes too long

View(coeficientes)

@@

write.csv(coeficientes, file="coef.csv")
write.csv(p, file="p-value.csv")

@@

```{r Extra: Mosaic Region-Dependence, echo=FALSE, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}
Data <- read_rds("BASE_PAPER.RDS")
Data <- Data %>% filter(JOVEN=="1")
Data <- Data %>% rename(COD_REG_ALU=codigo_region,Region=nombre_region)

df <- Data %>% filter(!is.na(COD_REG_ALU)) %>% filter(COD_REG_ALU>0)

df <- df %>%
  group_by(Region,COD_REG_ALU,COD_DEPE2) %>%
  summarise(count = n()) %>%
  mutate(Region.count = sum(count),
         prop = count/sum(count)) %>%
  ungroup()

#df$TIPO_INST_3[is.na(df$TIPO_INST_3)]="No Matriculado"
#df <- df %>% arrange(COD_REG_ALU)
df$COD_REG_ALU[df$COD_REG_ALU==15]=0.5
df$COD_REG_ALU[df$COD_REG_ALU==16]=7.5
df$COD_REG_ALU[df$COD_REG_ALU==14]=9.5
df$COD_REG_ALU[df$COD_REG_ALU==13]=5.5

df <- df %>% mutate(Region = ifelse(Region=="METROPOLITANA DE SANTIAGO", "RM",
                                  ifelse(Region=="VALPARAISO","VALPO",
                                         ifelse(Region =="BIOBIO", "BBIO",
                                                ifelse(Region=="LA ARAUCANIA", "ARAUC",
                                                       ifelse(Region=="LIBERTADOR GENERAL BERNARDO O'HIGGINS", "LGBO",
                                                              ifelse(Region=="LOS LAGOS","LAGOS",
                                                                     ifelse(Region=="COQUIMBO", "COQ",
                                                                            ifelse(Region=="ANTOFAGASTA","ANTOF",
                                                                                   ifelse(Region=="LOS RIOS", "RIOS",
                                                                                          ifelse(Region=="TARAPACA", "TPCA",
                                                                                                 ifelse(Region=="ATACAMA","ATCMA",
                                                                                                        ifelse(Region =="ARICA Y PARINACOTA", "AYP",
                                                                                                               ifelse(Region=="MAGALLANES Y DE LA ANTARTICA CHILENA","MAG", ifelse(Region=="AYSEN DEL GENERAL CARLOS IBANEZ DEL CAMPO", "AYSEN", Region)))))))))))))))

df <- df %>% mutate(COD_DEPE2 = ifelse(COD_DEPE2=="Municipal","Public",
                                                     ifelse(COD_DEPE2=="P.Pag", "Private",
                                                            ifelse(COD_DEPE2=="P.Sub","Semi-Private",COD_DEPE2))))

Fig_11=ggplot(df,
       aes(x = reorder(Region,COD_REG_ALU), y = prop, width = Region.count, fill =COD_DEPE2 )) + labs(fill="Dependence") +
  geom_bar(stat = "identity", position = "fill", colour = "black") +
  geom_text(aes(label = scales::percent(prop, accuracy = 1)), position = position_stack(vjust = 0.5), size=3, angle=90) + 
  facet_grid(~reorder(Region,COD_REG_ALU), scales = "free_x", space = "free_x") +
  scale_fill_brewer(palette = "Pastel1") + 
  theme_bw() + theme(strip.text.x = element_text(size = 10, colour = "black", angle = 90), 
                     legend.position = "top", axis.text = element_blank(), 
                     legend.text = element_text(size=14), legend.title = element_text(size=16),
                     axis.ticks = element_blank()) + 
  labs(y="", x="")

ggsave("/Users/bolea/Documents/GitHub/HE_Chile/Figures/Fig_11.eps",Fig_11, width=12.16, height=7.45, limitsize = FALSE)
ggsave("/Users/bolea/Documents/GitHub/HE_Chile/Figures/Fig_11.pdf",Fig_11, width=12.16, height=7.45, limitsize = FALSE)

```{r Extra: Rate by Region, echo=FALSE, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}

Data <- read_rds("BASE_PAPER.RDS")
Data <- Data %>% filter(JOVEN=="1")
Data <- Data %>% rename(COD_REG_ALU=codigo_region,Region=nombre_region)

#admission process = agno_egreso + 1

matriculado_region <- Data %>% 
  filter(JOVEN=="1") %>%
  group_by(COD_REG_ALU, Region, MATRICULADO, TIPO_INST_1) %>% summarise(N=n())

matriculado_region=dcast(matriculado_region,COD_REG_ALU + Region ~ TIPO_INST_1 + MATRICULADO)
matriculado_region <- matriculado_region %>% rename(Universidades=Universidades_1 , CFT=`Centros de Formación Técnica_1` ,IP=`Institutos Profesionales_1`)
matriculado_region <- matriculado_region %>% rename(No_Matriculados=NA_0)
matriculado_region <- matriculado_region %>% mutate(Total_Egresados=Universidades+CFT+IP+No_Matriculados)
matriculado_region <- matriculado_region %>% mutate(Total_Matriculados=Universidades+CFT+IP)
matriculado_region <- matriculado_region %>% filter(!is.na(COD_REG_ALU)) %>% filter(COD_REG_ALU>0)
matriculado_region <- matriculado_region %>% mutate(Tasa_Ingreso = Total_Matriculados/Total_Egresados*100)

matriculado_region <- matriculado_region %>% mutate(Region = ifelse(Region=="METROPOLITANA DE SANTIAGO", "RM",
                                  ifelse(Region=="VALPARAISO","VALPO",
                                         ifelse(Region =="BIOBIO", "BBIO",
                                                ifelse(Region=="LA ARAUCANIA", "ARAUC",
                                                       ifelse(Region=="LIBERTADOR GENERAL BERNARDO O'HIGGINS", "LGBO",
                                                              ifelse(Region=="LOS LAGOS","LAGOS",
                                                                     ifelse(Region=="COQUIMBO", "COQ",
                                                                            ifelse(Region=="ANTOFAGASTA","ANTOF",
                                                                                   ifelse(Region=="LOS RIOS", "RIOS",
                                                                                          ifelse(Region=="TARAPACA", "TPCA",
                                                                                                 ifelse(Region=="ATACAMA","ATCMA",
                                                                                                        ifelse(Region =="ARICA Y PARINACOTA", "AYP",
                                                                                                               ifelse(Region=="MAGALLANES Y DE LA ANTARTICA CHILENA","MAG", ifelse(Region=="AYSEN DEL GENERAL CARLOS IBANEZ DEL CAMPO", "AYSEN", Region)))))))))))))))

matriculado_region <- matriculado_region %>% rename(codigo_region=COD_REG_ALU)

x = generar_regiones(mapa = chilemapas::mapa_comunas)
x$codigo_region = as.numeric(x$codigo_region)
x <- left_join(x, matriculado_region)
x <- x %>% mutate(Zoom=ifelse(codigo_region<8 | codigo_region==15 | codigo_region==16 | codigo_region==13,1,0))

x <- x %>% mutate(Porc = paste0(round(Tasa_Ingreso,1),"%"))

bar = ggplot(data=x, aes(x=reorder(factor(Region),Tasa_Ingreso),y=Tasa_Ingreso, fill=Tasa_Ingreso))  + coord_flip() + theme_minimal() + geom_bar(stat="identity") + labs(x="Region",y="Enrolment Rate") + theme(legend.position = "none", axis.title = element_text(size=17), axis.text.y = element_text(size=14), axis.text.x = element_text(size=14)) + geom_text(aes(label = Porc), position = position_stack(vjust = 0.5), size = 5, color="black") + scale_y_continuous(expand = expansion(mult = c(0, .1)))+scale_fill_distiller(palette = "RdBu", direction=1,limits=c(40,63))
bar

>>>>

reg <- within(reg, ESTADO <- relevel(ESTADO, ref = "No Matriculado"))
reg = reg %>% filter(EDAD %in% c('16','17','18','19'))
reg <- within(reg, COD_DEPE2 <- relevel(COD_DEPE2, ref = "Municipal"))
reg$NOMBRE_REGION = factor(reg$NOMBRE_REGION)
reg <- within(reg, NOMBRE_REGION <- relevel(NOMBRE_REGION, ref = "METROPOLITANA DE SANTIAGO"))

m_logit <- multinom(ESTADO ~ EDAD  + NEM + GEN_ALU + COD_DEPE2 + factor(PostBeca) + factor(NOMBRE_REGION), data = reg)

@@

#Coeficientes of the table.
#command Summary takes too long
View(t(coeficientes))

@@

write.csv(t(coeficientes), file="coef.csv")
write.csv(t(p), file="p-value.csv")

@@
